\input pdfcolor.tex
\pdfoutput=1\relax
\pdfpagewidth=8.26in  
\pdfpageheight=11.69in 
\pdfcompresslevel=0   
\pdfinfo{
	/Author (R. Andrew Bailey)
	/Title  (My Resume)
	/Subject (Resume of R. Andrew Bailey) 
}
\font\hf = cmss8
\font\body = cmss9
\font\myname = cmss8 scaled \magstep3
\font\category = cmssbx10 scaled \magstep1
\font\position = cmssi8 scaled \magstep1
\font\anitem = cmss8 scaled \magstep1
\font\content = cmss8 
\nopagenumbers
\parindent = 0 in
\body
{ 
\hf
\parskip = 0 pt
\parindent = 4.75 in
\vskip 10 pt
4904 West Park Drve

Austin, TX 78731

617.459.0972

GooseYArd@gmail.com

}

\vskip 10 pt
{ \myname \centerline{R. Andrew Bailey} \par }
\vskip 10 pt
{\category Objective}
\vskip 9 pt
Seeking a position in Software Architecture or Engineering, specializing in very large distributed Unix systems.
\vskip 9 pt
{\category Clearances}
\vskip 9 pt
DoD Top Secret/SSBI, active, read out 3/23/2013.
\vskip 9 pt
{\category Employment/Experience}
\vskip 9 pt
{\anitem 1999 - 2013,	Akamai Technologies,	Cambridge, MA/Reston, VA}

{\position Senior Software Architect}

\item{$\bullet$} Managed a team of 13 developers responsible for delivering Akamai's managed CDN service (GCDS) to the United States Department of Defense.

\item{$\bullet$} Developed extensions to BIND9 to allow CDN operation in environments with centralized DNS.

\item{$\bullet$} Lead developer on Starbucks/iTunes in-store audio streaming and iheartradio.com mp3 streaming projects.

\item{$\bullet$} Developed software and tools for operation of the Akamai CDN's deployment of +150,000 physical servers.

\item{$\bullet$} Inventor of Akamai's patented remote operating system installation methodology.

\vskip 9 pt
{\anitem 1995 - 1999,	Marshall University Computer Center,	Huntington, WV}

{\position Senior Systems Programmer}

\item{$\bullet$} Oversaw design and installation of the University-wide Windows NT infrastructure, supporting over 30,000 users on several campuses. Development of systems to provide automated mass client installations.
\vskip 9 pt

{\category Qualifications}
\vskip 9 pt
\item{$\bullet$} 20 years experience programming, principally Python, C/C++, Go, Java and Perl, with an emphasis on quality through test-driven development.

\item{$\bullet$} Tools development for very large server deployments.

\item{$\bullet$} Multiprocess/Multithreaded Unix system programming with sockets, pthreads, Posix message queues, etc.

\item{$\bullet$} Extensive, packet-level experience with TCP/IP, focused on DNS and HTTP protocols and packet capture/analysis with libpcap and Dnet.

\item{$\bullet$} Security experience with PKI (generic x509 and DOD CAC) and SSL (Openssl and Gcrypt).

\item{$\bullet$} Extensive experience with the GNU toolchain, GCC, GNU Make, GNU Autoconf. Some experience with MSVC toolchain.

\item{$\bullet$} Extensive RDBMS programming experience with Oracle, Postgresql, DB2 and Mysql.

\item{$\bullet$} Release management with Perforce and git. 

\vskip 9pt
{\category Education}
\vskip 9 pt
{\anitem 1993 - 2002	Marshall University	Huntington, WV}

{\item{} Regents Bachelor of Arts, Cum Laude }

{\item{} Emphasis on Computer Science and Software Development }

{\item{} Deferred completion after accepting senior position at
Marshall in 1995. Completed remaining credits at Harvard University Summer and Extension schools in Cambridge, MA. }
\vskip 9pt
{\category References}
\item{} Available on request.
{
\hf
\vfill
\centerline{Revised 2013/07/25} 
}

\bye
